### 2025-01-21 documentation/supplement.tex
Fixed Typo in supplement.

\subsection{Safety}
Class 4 lasers are extremely dangerous. A reflection on a surface can be enough to inflict permanent eye damage. Safety protocols must be observed. Consult with your institution's environmental health and safety officer and take proper training before performing any work with a laser system. Learn from people experienced with these devices and work carefully.\newline
During alignment, always wear goggles (ours were ML1 by NoIR LaserShields with an optical density $>7$ in the relevant range around $920\text{ nm}$), remove jewelry and watches, only use-reflective tools, do not store unnecessary items on the optical table, and use the low laser power (“alignment mode”) whenever possible. Once the assembly progresses further, full power mode is necessary. Extra care must be taken then. Always use Laser Viewing Cards to track the laser. We use Thorlabs VRC4. Always be conscious where the beam is, and where the beam goes. The beam must be terminated in beam blockers and should be shielded whenever possible with opaque plastic or anodized aluminium tubes to increase safety.

>>>>

\subsection{Safety}
Class 4 lasers are extremely dangerous. A reflection on a surface can be enough to inflict permanent eye damage. Safety protocols must be observed. Consult with your institution's environmental health and safety officer and take proper training before performing any work with a laser system. Learn from people experienced with these devices and work carefully.\newline
During alignment, always wear goggles (ours were ML1 by NoIR LaserShields with an optical density $>7$ in the relevant range around $920\text{ nm}$), remove jewelry and watches, only use non-reflective tools, do not store unnecessary items on the optical table, and use the low laser power (“alignment mode”) whenever possible. Once the assembly progresses further, full power mode is necessary. Extra care must be taken then. Always use Laser Viewing Cards to track the laser. We use Thorlabs VRC4. Always be conscious where the beam is, and where the beam goes. The beam must be terminated in beam blockers and should be shielded whenever possible with opaque plastic or anodized aluminium tubes to increase safety.
